### 2020-11-02 S1_appendix.tex
revisions

\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}

@@

\section*{S1 Appendix: Rate quantiles}

@@

>>>>

\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\section*{S1 Appendix: Rate quantiles and operators }

@@

\clearpage
\section{Summary of proposal kernels}

Operators whose proposal kernels are affected by the decision to use a Bactrian kernel, as opposed to a uniform kernel, are specified below.

\begin{table}[h!]
\centering
\begin{tabular}{l p{3cm} l l}

 & Operator(s) & Proposal & Parameter $x$   \\
   \hline
 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}, \sigma$  \\
  \hline
 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\vec{\mathcal{R}}^{\,}, \sigma$   \\
  \hline
 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\vec{\mathcal{R}}^{\,}$  \\
  \hline
 4 & \texttt{ConstantDistance} \texttt{SimpleDistance} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
 \hline
 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}$  \\
 \hline
6 & \texttt{CisScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
\end{tabular}
\caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
 In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
 The scale size $s$ is tunable.
 \texttt{ConstantDistance} and \texttt{SimpleDistance} propose tree heights $t$.
  The \texttt{Interval} operator applies to rate quantiles and respects its domain i.e. $0 < x, x^\prime < 1$. }
\label{table:bactriankernels}
\end{table}

\clearpage
\section{Supplementary NER Algorithm}

A second NER algorithm is presented below. This operator was rejected by the screening protocol on simulated data.

\begin{algorithm}
\caption{The NER$\{ \mathcal{D}_{BC}, \mathcal{D}_{CE} \}$ operator.}
\begin{algorithmic}[1]

\Procedure{proposal}{$t_A$, $t_B$, $t_C$, $t_D$, $t_E$, $r_A$, $r_B$, $r_C$, $r_D$}

	\State
    \State $s\Sigma \leftarrow $ getRandomWalkSize() \Comment{Random walk size is 0 unless this is NERw}
    \State $t_D^\prime \leftarrow t_D + s\Sigma$ \Comment{Propose new node height for $D$}
    \State
    \State $r_A^\prime \leftarrow r_A$ \Comment{Propose new rates}
    \State $r_B^\prime \leftarrow \frac{r_B(t_D - t_B) + r_D(t_E - t_D) + r_D(t_E - t_D^\prime)}{t_D^\prime - t_B}$
    \State $r_C^\prime \leftarrow \frac{r_C(t_E - t_C) - r_D(t_E - t_D^\prime)}{t_D^\prime - t_C}$
    \State $r_D^\prime \leftarrow r_D$
    \State
    \State $|J| \leftarrow \frac{(t_D - t_B)(t_E - t_C)}{(t_D^\prime - t_B)(t_D^\prime - t_C)}$ \Comment{Calculate Jacobian determinant}
    \State \Return $(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J|)$

\EndProcedure

\end{algorithmic}
\label{alg:NER1}
\end{algorithm}
